### 2016-09-30 gamma.tex
Add link to gamma page for tan(x)
Wording

\begin{itemize}
\item
  SymPy Gamma displays integration and differentiation steps in detail, which
  can be viewed in Figure~\ref{fig:integralsteps}.\par
  {
    \centering
    \includegraphics[width=0.7\textwidth]{integral_steps.png}
    \captionof{figure}{Integral steps of $\tan (x)$}\label{fig:integralsteps}
    \par
  }
\item
  SymPy Gamma displays the factor tree diagrams for different numbers.
\item
  SymPy Gamma saves user search queries, and offers many such similar features
  for free, which Wolfram\textbar{}Alpha only offers to its paid users.
\end{itemize}
Every input query from the user on SymPy Gamma is first parsed by its
own parser capable of handling several different forms of function names
which SymPy as a library does not support. For instance, SymPy Gamma
supports queries like \texttt{sin\ x}, whereas SymPy will only recognise
\verb|sin(x)|.

>>>>

\begin{itemize}
\item
  SymPy Gamma displays integration and differentiation steps in detail, as
  demonstrated in Figure~\ref{fig:integralsteps}.\par
  {
    \centering
    \includegraphics[width=0.7\textwidth]{integral_steps.png}
    \captionof{figure}{\href{http://www.sympygamma.com/input/?i=tan(x)}{Integral steps of $\tan (x)$}}\label{fig:integralsteps}
    \par
  }
\item
  SymPy Gamma displays the factor tree diagrams for different numbers.
\item
  SymPy Gamma saves user search queries, and offers many such similar features
  for free, which Wolfram\textbar{}Alpha only offers to its paid users.
\end{itemize}
Every input query from the user on SymPy Gamma is first parsed by its
own parser capable of handling several different forms of function names
which SymPy as a library does not support. For instance, SymPy Gamma
supports queries like \texttt{sin\ x}, whereas SymPy will only recognise
\verb|sin(x)|.
